\showyourwork: a workflow for open source scientific articles

### 2021-12-21 src/ms.tex
more words

% Author list
\author[0000-0002-0296-3826]{Rodrigo Luger}

@@

\section{Starting a project}
\label{sec:start}
%
Users can start a new project by \href{https://github.com/rodluger/showyourwork-template/generate}{creating a fresh repository based on the \texttt{showyourwork-template}}.
This will create a new repository under the user's \texttt{GitHub} account and trigger a \texttt{GitHub Action} that will finish the setup process.
After a few minutes...
%
\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{static/banner.png}
        \caption{
            The default \texttt{README} banner in a repository instantiated from the \texttt{showyourwork-template}, with links to the \texttt{GitHub Action} build logs, a tarball containing the \texttt{TeX} source for the article, a directed acyclic graph (DAG) of the build process, and the compiled article PDF, respectively.
        }
        \label{fig:banner}
    \end{centering}
\end{figure}
%

>>>>

% Author list
\author[0000-0002-0296-3826]{Rodrigo Luger}
\author{Others TBD}

@@

\section{Prerequisites}
\label{sec:prereq}
Conda. Linux/UNIX/Mac. GitHub account.

\section{Starting a project}
\label{sec:start}
%
Users can start a new project by \href{https://github.com/rodluger/showyourwork-template/generate}{creating a fresh repository based on the \texttt{showyourwork-template}}.
This will create a new repository under the user's \texttt{GitHub} account and trigger a \texttt{GitHub Action} that will finish the setup process and build a skeleton version of the paper.
After a few minutes, a banner will appear on the repository's main page with links to the build logs and the compiled article PDF (see Figure~\ref{fig:banner}).
%
\begin{figure}[th!]
    \begin{centering}
        \includegraphics[width=\linewidth]{static/banner.png}
        \caption{
            The default \texttt{README.md} banner in a repository instantiated from the \texttt{showyourwork-template}, with links to the \texttt{GitHub Action} build logs, a tarball containing the \texttt{TeX} source for the article, a directed acyclic graph (DAG) of the build process, and the compiled article PDF, respectively.
        }
        \label{fig:banner}
    \end{centering}
\end{figure}
%
At this point, the repository can be cloned locally, e.g.,
%
\begin{lstlisting}[
    style=bash,
    otherkeywords={user,repo},
    emph={user,repo},
    emphstyle={\color{lsthilite}}
]
git clone https://github.com/user/repo
cd repo
\end{lstlisting}
%
where {\color{lsthilite}\texttt{user}} and {\color{lsthilite}\texttt{repo}} are the \texttt{GitHub} user name and repository name, respectively.
The user may now edit the manuscript (\texttt{src/ms.tex}), add figure scripts to the \texttt{src/figures} directory, etc. (see \S\ref{sec:struct}).
The article may be built locally by running \texttt{make} in the top level directory (see \S\ref{sec:local-builds}).
Upon committing and pushing the changes to the remote repository, the \texttt{GitHub Action} will be triggered automatically, generating a new article PDF in sync with the latest changes (see \S\ref{sec:remote-builds}).

\section{Reproducing a project}
\label{sec:reproduce}
%
Any project based on \showyourwork can be reproduced by cloning its \texttt{GitHub} repository and running \texttt{make}:
%
\begin{lstlisting}[
    style=bash,
    otherkeywords={user,repo},
    emph={user,repo},
    emphstyle={\color{lsthilite}}
]
git clone https://github.com/user/repo
cd repo
make
\end{lstlisting}
%
This will create a fresh \texttt{conda} environment and run the \texttt{Snakemake} workflow to build the article from scratch, which may entail the execution of computationally-intensive scripts/tasks.
These may sometimes be skipped by instead running
%
\begin{lstlisting}[
    style=bash
]
make fast
\end{lstlisting}
%
which will download any available intermediate files from \texttt{Zenodo} instead of generating them from scratch. See \S\ref{sec:local-builds} for details.

\section{Local builds}
\label{sec:local-builds}
%
Coming soon.

\section{Remote builds}
\label{sec:remote-builds}
%
Coming soon.
